\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: MIT 6.006 Introduction to Algorithms}
\author{MIT course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://ocw.mit.edu/courses/6-006-introduction-to-algorithms-fall-2011/}

\textbf{Why this course is in the system.} Algorithm foundation for SLAM graph search, data structures, complexity, and validation scripts.

\textbf{Learning output.} Write a graph, search, and heap formula page, then connect it to simctl data structures.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Discrete math
  \item Python or pseudocode
  \item Proof by induction
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  T(n)=aT(n/b)+f(n)\\
  d[v]=\min_{(u,v)\in E}\{d[u]+w(u,v)\}\\
  O((V+E)\log V)\\
  \operatorname{heapify}=O(\log n)
\end{align*}

\section*{Visual page}
Draw a graph search frontier and show why a priority queue changes the exploration order.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page MIT-A001: asymptotic notation
  \item Page MIT-A002: graph search and Dijkstra
\end{itemize}

\section*{Web interaction}
A draggable graph where edge weights update the shortest-path table.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & MIT EECS -> 6.006 algorithms \\
Notion & Solved problem evidence and algorithm notes. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
