\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: Tsinghua Automation undergraduate program PDF}
\author{Tsinghua course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://www.tsinghua.edu.cn/jxjywj/bkzy2023/zxzy/27.pdf}

\textbf{Why this course is in the system.} Undergraduate curriculum source for signals, automatic control, pattern recognition, machine learning, and robotics.

\textbf{Learning output.} Create a GoodNotes undergraduate spine page with prerequisites, formulas, and outputs.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Advanced mathematics
  \item Linear algebra
  \item Programming
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  y(t)=\int_{-\infty}^{\infty}x(\tau)h(t-\tau)d\tau\\
  \dot{\bm{x}}=A\bm{x}+B\bm{u}\\
  \min_{\theta}\frac{1}{N}\sum_{i=1}^{N}\ell(f_{\theta}(\bm{x}_i),y_i)\\
  s\bm{u}=K[R\;\bm{t}]\bm{X}
\end{align*}

\section*{Visual page}
Turn the undergraduate program into a prerequisite graph instead of a calendar.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page THU-B001: undergraduate course spine
  \item Page THU-B002: where each formula first appears
\end{itemize}

\section*{Web interaction}
A filterable curriculum map by math, control, AI, robotics, and spatial intelligence.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & Tsinghua Automation -> undergraduate spine \\
Notion & Course-source evidence and next PDF expansion status. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
