\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: Stanford CS224N Natural Language Processing with Deep Learning}
\author{Stanford course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://web.stanford.edu/class/cs224n/}

\textbf{Why this course is in the system.} Language and representation learning for Hermes interaction, tutoring, and multimodal reasoning.

\textbf{Learning output.} Keep it as the NLP and Transformer side line after the spatial geometry first round.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Linear algebra
  \item Probability
  \item Neural networks
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  \operatorname{sim}(\bm{u},\bm{v})=\frac{\bm{u}^{\mathsf T}\bm{v}}{\|\bm{u}\|\|\bm{v}\|}\\
  \operatorname{Attention}(Q,K,V)=\operatorname{softmax}\left(\frac{QK^{\mathsf T}}{\sqrt{d_k}}\right)V\\
  \bm{h}_t=f(\bm{x}_t,\bm{h}_{t-1})\\
  L=-\sum_t \log p(y_t|y_{<t},\bm{x})
\end{align*}

\section*{Visual page}
Show tokens -> embeddings -> attention map -> context vector -> prediction.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page ST-NLP001: embeddings
  \item Page ST-NLP002: attention
  \item Page ST-NLP003: sequence loss
\end{itemize}

\section*{Web interaction}
An attention heatmap that highlights which token reads which token.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & Stanford NLP -> CS224N \\
Notion & Hermes interaction bridge and assignment status. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
