\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: Tsinghua control spine}
\author{Tsinghua course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://www.au.tsinghua.edu.cn/}

\textbf{Why this course is in the system.} Connect automatic control, modern control, optimization, estimation, robust control, and nonlinear control.

\textbf{Learning output.} Generate individual guided PDFs in batches, with the roadmap as the current index.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Differential equations
  \item Signals and systems
  \item Matrix rank and eigenvalues
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  \mathcal{C}=[B\;AB\;\cdots\;A^{n-1}B],\quad \operatorname{rank}(\mathcal{C})=n\\
  \mathcal{O}=\begin{bmatrix}C\\CA\\\vdots\\CA^{n-1}\end{bmatrix}\\
  V(\bm{x})=\bm{x}^{\mathsf T}P\bm{x},\quad \dot{V}(\bm{x})<0\\
  A^{\mathsf T}P+PA-PBR^{-1}B^{\mathsf T}P+Q=0
\end{align*}

\section*{Visual page}
Draw controllability, observability, stability, and LQR as four connected gates.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page THU-C001: controllability and observability
  \item Page THU-C002: Lyapunov and LQR
\end{itemize}

\section*{Web interaction}
A rank-gate visual where the learner toggles B and C and watches rank change.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & Control Engineering -> Tsinghua control spine \\
Notion & Mastery levels for control gates. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
