\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: Stanford AA228/CS238 Decision Making under Uncertainty}
\author{Stanford course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://web.stanford.edu/class/aa228/}

\textbf{Why this course is in the system.} MDPs, POMDPs, planning, risk, and decision-making under uncertainty.

\textbf{Learning output.} Connect it to world models and autonomous-driving decision chapters.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Probability
  \item Dynamic programming
  \item Basic optimization
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  V^{\star}(s)=\max_a\left[R(s,a)+\gamma\sum_{s'}P(s'|s,a)V^{\star}(s')\right]\\
  \pi^{\star}(s)=\arg\max_a Q^{\star}(s,a)\\
  b'(s')=\eta O(o|s',a)\sum_s P(s'|s,a)b(s)\\
  \mathbb{E}\left[\sum_{t=0}^{\infty}\gamma^t r_t\right]
\end{align*}

\section*{Visual page}
Draw state, action, transition, observation, belief, and value as a decision loop.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page ST-DM001: MDP
  \item Page ST-DM002: POMDP belief update
  \item Page ST-DM003: risk and planning
\end{itemize}

\section*{Web interaction}
A grid-world widget where transition uncertainty changes the best action.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & Stanford Decision Making -> AA228 CS238 \\
Notion & World-model decision bridge. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
