\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: MIT Missing Semester}
\author{MIT course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://missing.csail.mit.edu/}

\textbf{Why this course is in the system.} Engineering tools course for Git, shell, debugging, data processing, and learning-system maintenance.

\textbf{Learning output.} Use Notion as the tool readiness checklist so environment blockers are visible.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Terminal basics
  \item Files and paths
  \item Git basics
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  \text{pipeline}=f_n\circ f_{n-1}\circ\cdots\circ f_1\\
  \text{commit}=H(\text{tree},\text{parents},\text{message})\\
  \text{debugging}=\text{reproduce}\rightarrow\text{isolate}\rightarrow\text{verify}\\
  \text{automation}=\text{input}\rightarrow\text{script}\rightarrow\text{checked output}
\end{align*}

\section*{Visual page}
Draw shell, editor, git, tests, and browser as one reproducible learning loop.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page MIT-T001: shell and git workflow
  \item Page MIT-T002: debugging checklist
\end{itemize}

\section*{Web interaction}
A command checklist that marks environment readiness.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & MIT Tools -> Missing Semester \\
Notion & Tool blocker, command evidence, and next action. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
