\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb,bm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}

\title{Cyrus Guided Notes: Tsinghua Automation official site}
\author{Tsinghua course pack}
\date{2026-05-15}

\begin{document}
\maketitle

\section*{Course source}
\textbf{Official source:} \url{https://www.au.tsinghua.edu.cn/}

\textbf{Why this course is in the system.} Department and research-direction entry point for automation, control science, and intelligent systems.

\textbf{Learning output.} Build an Obsidian field map covering math, signals, control, intelligence, and robotics.

\section*{Prerequisite checkpoint}
\begin{itemize}[leftmargin=1.4em]
  \item Linear algebra
  \item Calculus
  \item Probability and signals
\end{itemize}

\section*{Formula checkpoint}
Do not memorize these first. Read each formula as a sentence: what changes, what is observed, what is optimized, and what output it produces.
\begin{align*}
  \dot{\bm{x}}=A\bm{x}+B\bm{u}\\
  \bm{y}=C\bm{x}+D\bm{u}\\
  \mathcal{C}=[B\;AB\;\cdots\;A^{n-1}B]\\
  \hat{\bm{x}}_{k|k}=\hat{\bm{x}}_{k|k-1}+K_k(\bm{z}_k-H\hat{\bm{x}}_{k|k-1})
\end{align*}

\section*{Visual page}
Draw one department map: math -> signals -> control -> estimation -> robotics -> spatial intelligence.

\section*{GoodNotes pages}
\begin{itemize}[leftmargin=1.4em]
  \item Page THU-000: automation field map
  \item Page THU-001: state/input/output vocabulary
\end{itemize}

\section*{Web interaction}
A clickable concept graph that opens the correct course pack node.

\section*{Obsidian and Notion}
\begin{tabular}{p{0.22\linewidth}p{0.68\linewidth}}
\toprule
Layer & Output \\
\midrule
Obsidian & Tsinghua Automation -> field map \\
Notion & Source status, syllabus status, and expansion blocker. \\
\bottomrule
\end{tabular}

\section*{First study move}
Open the official source, copy the prerequisite checkpoint into GoodNotes, then write one formula in your own words before watching or reading more.

\end{document}
